Modelling

### 2022-04-05 analysis/Modelling Final.Rmd
Added four more models to modelling script

```{r}
# Load packages
library(dplyr)
library(tidyr)
library(kableExtra)
library(nnet)
library(plm)
library(readxl)
options(scipen=999)
# load Brazil data
pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
pop <-  pop %>% select(-c(title, date, text, location))
# Load Amazon context data
ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")
# wrangle dataset
ama_model1 <-  ama %>% select(-c(title, date, text, false_positives)) %>% 
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = as.factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
                                      mixed_type == '0_0_0_0' ~ "Other",
                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                            mixed_type) ~ "Other Types")))
# Model without any controls or normalization or time effects
model1 <- multinom(mx_cat ~ location_cat, data = ama_model1)
summary(model1)
# Get p-values
p_values1 <- round((1 - pnorm(abs(summary(model1)$coefficients/summary(model1)$standard.errors)))*2, 5)
p_values1 <- data.frame(ifelse(p_values1 < 0.05, paste0(p_values1, "** Coef (",round(summary(model1)$coefficients, 5), ")"),
                               p_values1))[,-1]
# Get a decent table
kableExtra::kable(x = p_values1, caption = "P values for Model 1",
                  col.names = c("Brasilia", "International", "Non-AM State", "TV and Radio"))
#stargazer::stargazer(model1, type="text", add.lines = nrow(model1$residuals))
```

@@

```{r}
ama_model2 <- ama_model1 %>% 
         mutate(election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0)) # election year
# deforestation yearly (year before) - load data and merge
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>% # yearly deforestation rates only come out the year after
  rename(def_year = `area km²`)
ama_model2 <- dplyr::left_join(ama_model2, amazon_def_year, by = "year") # merge
# inflation rates per year Brazil (average for year - but could be change)
average_inflation_year_BR <- read_excel("data/average_inflation_year_BR.xlsx") # source world bank
ama_model2 <- dplyr::left_join(ama_model2, average_inflation_year_BR, by = "year") # merge
# Model with some controls
model2 <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model2)
summary(model2)
# Get p-values
p_values2 <- round((1 - pnorm(abs(summary(model2)$coefficients/summary(model2)$standard.errors)))*2, 5)
p_values2 <- data.frame(ifelse(p_values2 < 0.05, paste0(p_values2, "** Coef (",round(summary(model2)$coefficients, 5), ")"),
                               p_values2))[,-1]
# Get a decent table
kableExtra::kable(x = p_values2, caption = "P values for Model 2",
                  col.names = c("Brasilia", "International", "Non-AM State", "TV and Radio",
                                "Election_Year", "Deforastion_year", "Avg_inflation"))
```

@@

>>>>

```{r}
# Load packages
library(dplyr)
library(tidyr)
library(kableExtra)
library(nnet)
library(plm)
library(readxl)
library(stargazer)
options(scipen=999)
# load Brazil data
pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
pop <-  pop %>% select(-c(title, date, text, location))
# Load Amazon context data
ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")
# wrangle dataset
ama_model1 <-  ama %>% select(-c(title, date, text, false_positives)) %>% 
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = as.factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
                                      mixed_type == '0_0_0_0' ~ "Other",
                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                            mixed_type) ~ "Other Types")))
# Model without any controls or normalization or time effects
model1 <- multinom(mx_cat ~ location_cat, data = ama_model1)
summary(model1)
# Get p-values
p_values1 <- round((1 - pnorm(abs(summary(model1)$coefficients/summary(model1)$standard.errors)))*2, 5)
p_values1 <- data.frame(ifelse(p_values1 < 0.05, paste0(p_values1, "** Coef (",round(summary(model1)$coefficients, 5), ")"),
                               p_values1))[,-1]
# Get a decent table
kableExtra::kable(x = p_values1, caption = "P values for Model 1",
                  col.names = c("Brasilia", "International", "Non-AM State", "TV and Radio"))
#stargazer::stargazer(model1, type="text", add.lines = nrow(model1$residuals))
```

@@

```{r}
ama_model2 <- ama_model1 %>% 
         mutate(election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0)) # election year
# deforestation yearly (year before) - load data and merge
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>% # yearly deforestation rates only come out the year after
  rename(def_year = `area km²`)
ama_model2 <- dplyr::left_join(ama_model2, amazon_def_year, by = "year") # merge
# inflation rates per year Brazil (average for year - but could be change)
AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds") # source world bank
ama_model2 <- dplyr::left_join(ama_model2, AAI, by = "year") # merge
# Model with some controls
model2 <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model2)
summary(model2)
# Get p-values
p_values2 <- round((1 - pnorm(abs(summary(model2)$coefficients/summary(model2)$standard.errors)))*2, 5)
p_values2 <- data.frame(ifelse(p_values2 < 0.05, paste0(p_values2, "** Coef (",round(summary(model2)$coefficients, 5), ")"),
                               p_values2))[,-1]
# Get a decent table
kableExtra::kable(x = p_values2, caption = "P values for Model 2",
                  col.names = c("Brasilia", "International", "Non-AM State", "TV and Radio",
                                "Election_Year", "Deforastion_year", "Avg_inflation"))
```

@@

# Last few models

With controls and mix types but no president...

```{r}
ama_model5 <- ama_model2 %>%
  filter(location_cat != "Non Identified",
         mx_cat != "Other Types") %>% 
  mutate(mx_cat = relevel(mx_cat, ref = "Pure Conservation"))
# model
model5 <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model5)
summary(model5)$coefficients
# Vizualize (just keep log odds and significance stars)
stargazer::stargazer(model5, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
                     covariate.labels = c("Brasilia", "International", "Non-AM state",
                                "Election", "Deforestation", "Inflation"),
                     column.labels = c("EI-SD", "EI-Con", "Other", "EI", "SD", "Sov",
                                       "SD-Con", "Sov-Con", "Sov-EI", "SD-EI-Con"),
                     dep.var.labels.include = FALSE)
```

With controls and mix types and president...

```{r}
# model
model6 <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI + president, data = ama_model5)
summary(model6)$coefficients
# Vizualize (just keep log odds and significance stars)
stargazer::stargazer(model6, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
                     covariate.labels = c("Brasilia", "Int.", "Non-AM state", 
                                          "Election", "Def.", "Inflation", "Collor", "Rousseff", "Cardoso",
                                          "Franco", "Lula", "Sarney", "Temer"),
                     column.labels = c("EI-SD", "EI-Con", "Other", "EI", "SD", "Sov",
                                       "SD-Con", "Sov-Con", "Sov-EI", "SD-EI-Con"),
                     dep.var.labels.include = FALSE)
```

I do not know here... I few there is a lot of significant things but I do not think we should include speaker.

Let's try to recode variables and run the same model.

```{r}
sov2 <- ama %>% 
  filter(sov==1) %>%
  select(c(sov, location_cat, year, president))%>%
  mutate(prob_constr=case_when(sov=="1"~ "sov")) %>%
  select(-c(sov))
ei2 <- ama %>% 
  filter(EI==1)%>%
  select(c(EI, location_cat, year, president))%>%
  mutate(prob_constr=case_when(EI=="1"~ "EI")) %>%
  select(-c(EI))
sd2 <- ama %>% 
  filter(SD==1)%>%
  select(c(SD, location_cat, year, president))%>%
  mutate(prob_constr=case_when(SD=="1"~ "SD")) %>%
  select(-c(SD))
con2 <- ama %>% 
  filter(con==1)%>%
  select(c(con, location_cat, year, president))%>%
  mutate(prob_constr=case_when(con=="1"~ "con")) %>%
  select(-c(con))
other2 <- ama %>% 
  filter(other==1)%>%
  select(c(other, location_cat, year, president))%>%
  mutate(prob_constr = case_when(other=="1"~ "other")) %>%
  select(-c(other))
ama_model7 <- rbind(sov2, con2, ei2, sd2, other2) %>% 
  mutate(prob_constr = as.factor(prob_constr),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))  %>% # election year
  filter(location_cat != "Non Identified")
# deforestation yearly (year before)
ama_model7 <- dplyr::left_join(ama_model7, amazon_def_year, by = "year") # merge
# inflation rates per year Brazil (average for year - but could be change)
ama_model7 <- dplyr::left_join(ama_model7, AAI, by = "year") # merge
# model
model7 <- multinom(prob_constr ~ location_cat + election_year + def_year + AAI, data = ama_model7)
summary(model7)$coefficients
# Vizualize (just keep log odds and significance stars)
stargazer::stargazer(model7, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
                     covariate.labels = c("Brasilia", "International", "Non-AM state",
                                          "Election", "Deforestation", "Inflation"),
                     column.labels = c("EI", "Other", "SD", "Sov"),
                     dep.var.labels.include = FALSE)
```

I do not know if the results differ that much that we should change, what do you think?

```{r}
# model
model8 <- multinom(prob_constr ~ location_cat + election_year + def_year + AAI + president, data = ama_model7)
summary(model8)$coefficients
# Vizualize (just keep log odds and significance stars)
stargazer::stargazer(model8, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
                     covariate.labels = c("Brasilia", "International", "Non-AM state",
                                          "Election", "Deforestation", "Inflation", "Collor", "Rousseff", "Cardoso",
                                          "Franco", "Lula", "Sarney", "Temer"),
                     column.labels = c("EI", "Other", "SD", "Sov"),
                     dep.var.labels.include = FALSE)
```
